\documentclass[10pt]{article}
\usepackage{my_packages}
\usepackage{tikz_packages}
%% url smaller font.
\makeatletter
\def\url@leostyle{%
\@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
\makeatother
\urlstyle{leo}

%\usepackage[all,import]{xy}

\renewcommand{\baselinestretch}{1.2}
\date{}

\renewcommand{\thesubsection}{\arabic{subsection}. }
\renewcommand{\thesubsubsection}{\arabic{subsection}.\arabic{subsubsection} }

\theoremstyle{definition}
\newtheorem{prob}{Problem}[section]
%\renewcommand{\theprob}{\arabic{section}.\arabic{prob}}
\renewcommand{\theprob}{\arabic{prob}}

\newenvironment{subprob}%
{\renewcommand{\theenumi}{\alph{enumi}}\renewcommand{\labelenumi}{(\theenumi)}\begin{enumerate}}%
{\end{enumerate}}%


\begin{document}

\pagestyle{empty}
\section*{MAE3134: Homework 6}
\vspace*{-0.4cm}
\noindent{Due date: 12 April 2018}%\\%\vspace*{0.5cm}

\begin{prob}
    A system is defined by the transfer function
    \begin{align*}
        G(s) = \frac{50}{\parenth{s+1}\parenth{s+2}\parenth{s+10}} .
    \end{align*}

    \begin{subprob}
        \item Sketch the Bode diagram for this system using the approximations from class and the semi-log graph paper provided on Blackboard.
        \item Find the analytical expressions for the frequency response, magnitude, and phase response functions.
        \item Using a computer program, find the magnitude and phase of the system for a range of frequencies between \( \SI{0.1}{\hertz} \leq \omega \leq \SI{100}{\hertz}\).
        \item Plot these values on your Bode diagram and  estimate the maximum error in decibels and degrees between the true response and your approximations.
            Give the frequencies at which the maximum error occurs.
    \end{subprob}
\end{prob}

\begin{prob}
   Consider the system with the transfer function
   \begin{align*}
        G(s) = \frac{2 \parenth{s + 10}}{\parenth{s+1}{s+2}}.
   \end{align*}
   \begin{subprob}
        \item Sketch the Bode diagram for this system using the approximations from class and the semi-log graph paper provided on Blackboard.
        \item Without doing any calculations, find the steady-state output response for an input signal of \( u = \cos t \).
        \item Using the Laplace transform, calculate the output response.
        \item Verify your previous solutions using a computer program of your choice.
        \item Use a computer program to generate the true Bode plot and transfer these results to your approximation.
            Estimate the maximum errors in magnitude and phase and the frequencies at which they occur.
   \end{subprob}
\end{prob}

\end{document}
